%%%%
% MTecknology's Resume
%%%%
% Author: George Fam
% License: CC-BY-4
% - https://creativecommons.org/licenses/by/4.0/legalcode.txt
%%%%
\documentclass[letterpaper,10pt]{article}
\usepackage{mteck}
\usepackage{fancyhdr}

%===================%
% George Fam's Resume %
%===================%

%\numberedPages % NOTE: lastpage requires a second build
%\documentFooter{\tab \thepage \ / 2} % Does similar without using lastpage
\begin{document}
  %---------%
  % Heading %
  %---------%
  \documentTitle{George Fam}{
    % Web Version
    %\raisebox{-0.05\height} \faPhone\ [redacted - web copy] ~
    %\raisebox{-0.15\height} \faEnvelope\ [redacted - web copy] ~
    %%
    \href{tel:5146639709}{
      \raisebox{-0.05\height} \faPhone\ 514-663-9709} ~ | ~
    \href{mailto:george.fam@famcode.net}{
      \raisebox{-0.15\height} \faEnvelope\ george.fam@famcode.net} ~ | ~
    \href{https://www.linkedin.com/in/george-fam/}{
      \raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/george-fam} ~ | ~
    \href{https://www.github.com/George-Fam}{
      \raisebox{-0.15\height} \faGithubSquare\ github.com/George-Fam}
  }

  %---------%
  % Summary %
  %---------%

  \tinysection{Summary}
  Computer science and software engineering student at UQAM, passionate about software development, system administration, and teaching computer science. As a teaching assistant, I support students in labs and assess projects and tests, developing skills in pedagogy and technical explanation. My experience in pharmacy has also strengthened my communication and problem-solving abilities.

  %-----------%
  % Education %
  %-----------%

  \section{Education}

  \headingBf{Bachelor's Degree, Computer Science and Software Engineering}{2023 -- Ongoing} % Note: Adding year(s) exposes an implied age
  \headingIt{UQÀM | Université de Québec à Montréal}{}
  \vspace{10pt}
  \headingBf{Double DEC, Science and Social Science}{2023} % Note: Adding year(s) exposes an implied age
  \headingIt{CEGEP John Abbott}{}

  %--------%
  % Skills %
  %--------%

  \section{Skills}

  \begin{multicols}{2}
    \begin{itemize}[itemsep=-2px, parsep=5pt, leftmargin=75pt]
      \item[\textbf{Prog. Lang.}] Java, C, Bash, HTML/CSS/JS
      \item[\textbf{Databases}] Oracle SQL, SQLite
      \item[\textbf{Tools}] Git, Maven, Jira, Docker, Podman      
      \item[\textbf{Tests}] JUnit, BATS
      \item[\textbf{OS}]  Windows, Linux (Arch, Debian, Ubuntu)
      \item[\textbf{Methodologies}]  Scrum, Kanban, Agile
      \item[\textbf{Soft Skills}]  Communication, Teamwork, Conflict Resolution, Active Listening, Customer Service
      \item[\textbf{Pharmacy}]  RxPro, AssystRx, Ubiq, Empego, Magistral Meds, Medication Ordering, Prescription Preparation
      \item[\textbf{Languages}]  Français, Anglais, Arabe
    \end{itemize}
  \end{multicols}

  %------------%
  % Experience %
  %------------%

  \section{Experience}

  \headingBf{Computer Science Teaching Assistant}{Oct. 2024 -- Present}
  \headingIt{UQÀM | Université de Québec à Montréal}{}
  \begin{resume_list}
    \itemTitle{Lab Demonstrator}
    \item Providing hands-on guidance to students by explaining concepts and answering technical questions
    \begin{itemize}
        \item INF2120 — Programming II (Summer 2025)
        \item INF1070 — System Usage and Administration (Winter 2025)
        \item INF2050 — Software Dev. Tools and Practices (Winter 2025)
    \end{itemize}
  \vspace{3pt}
  
    \itemTitle{Exam Grader}
    \item Ensuring rigorous and objective grading in accordance with established guidelines
    \begin{itemize}
        \item INF2050 — Software Dev. Tools and Practices (Fall 2024, Winter 2025)
    \end{itemize}
  \end{resume_list}

  \headingBf{Pharmacy Technician}{Sept. 2022 -- Present}
  \headingIt{BeLocum}{Aug. 2023 -- Present}
  \headingIt{Jean Coutu}{Sept. 2022 -- Feb. 2025}
  \begin{resume_list}
    \item Accurately and efficiently interpret and input prescriptions using RxPro, AssystRx, and Ubiq
  \end{resume_list}

  \headingBf{Tutor}{Oct. 2022 -- June 2023}
  \headingIt{Pierrefonds Community Project}{}
  \begin{resume_list}
    \item Design and lead engaging extracurricular tutoring sessions for students
    \item Assist students with homework and exam preparation
    \item Organize small group learning sessions and interactive games to boost academic motivation
    \item Develop and implement additional exercises to improve student understanding
    \item Correct exercises to help students identify and learn from their mistakes
  \end{resume_list}

  \headingBf{Assistant Manager}{July 2018 -- July 2020}
  \headingIt{Couche-Tard}{}
  \begin{resume_list}
    \item Train new team members on point-of-sale systems and customer service
    \item Prepare financial reports and make bank deposits.
  \end{resume_list}
  \pagebreak

    %----------------------------%
  % Extracurricular Activities %
  %----------------------------%

  \section{Projects}

  \headingBf{INF2120 (Programming  II)}{Java, JUnit, Swing}
  \begin{resume_list}
    \item Develop a virtual robot emulator \href{https://github.com/George-Fam/Robot-Controller-Emulator}{\faGithubSquare George-Fam/Robot-Controller-Emulator}
    \vspace{2pt}
    \item Develop features for a Tower Defense-style game using Swing \href{https://github.com/George-Fam/java-tower-defense}{\faGithubSquare\ George-Fam/java-tower-defense}
    \vspace{2pt}
    \item Design and manage data structures such as disjoint sets to model sorted intervals \href{https://github.com/George-Fam/java-disjoint-interval-set}{\faGithubSquare\ George-Fam/java-disjoint-interval-set}
    \vspace{2pt}
    \item Implement algorithms based on provided interfaces
    \vspace{2pt}
    \item Create unit tests to ensure the robustness and reliability of implemented features
  \end{resume_list}

  \headingBf{INF2050 (Software Dev. Tools and Practices)}{Java, JUnit, Maven}
  \begin{resume_list}
    \item Develop an application to calculate the property value of lands based on input JSON data, with JSON output generation \href{https://github.com/George-Fam/land-value-analyzer}{\faGithubSquare George-Fam/land-value-analyzer}
    \vspace{2pt}
    \item Use Maven for dependency management, compilation, and generating executable JAR files
    \vspace{2pt}
    \item Write and execute automated unit tests using Maven and JUnit
  \end{resume_list}
  
  \headingBf{INF3135 (Software Construction and Maintenance)}{C, Bash, BATS}
  \begin{resume_list}
    \item Develop the video game \textit{Circle}, inspired by \textit{Super Hexagon}, using the SDL2 library for graphic programming and animation \href{https://github.com/George-Fam/Circles}{\faGithubSquare George-Fam/Circles}
    \vspace{2pt}
    \item Use Bash and BATS to write and automate tests
    \vspace{2pt}
    \item Manage the project using Git and a collaborative approach with branching, merge requests, and clear versioning
  \end{resume_list}
  
 %----------------------------%
  % Volunteering %
  %----------------------------%

  \section{Social Involvement}

  \headingBf{Volunteer Tutor}{2016 -- 2017 \& 2022}
  \headingIt{Pierrefonds Community Project}{Jan. 2022 -- June 2022}
  \headingIt{St-Georges High School}{Oct. 2016 -- March 2017}
  \begin{resume_list}
    \item Assist students with their homework
    \item Explain math and science concepts in simple terms
  \end{resume_list}
  
  \headingBf{Volunteer Patient Activity Attendant}{Oct. 2016 -- Feb. 2017}
  \headingIt{Sainte-Anne Hospital}{}
\begin{resume_list}
    \item Accompany and assist patients in their routines and daily activities
    \item Participate in organizing recreational activities, such as bingo games
\end{resume_list}

\end{document}
