%%%%
% MTecknology's Resume
%%%%
% Author: George Fam
% License: CC-BY-4
% - https://creativecommons.org/licenses/by/4.0/legalcode.txt
%%%%
\documentclass[letterpaper,10pt]{article}
\usepackage{mteck}
\usepackage{fancyhdr}

%===================%
% George Fam's Resume %
%===================%

\begin{document}
%---------%
% Heading %
%---------%
\documentTitle{George Fam}{
	\href{tel:5146639709}{
	\raisebox{-0.05\height} \faPhone\ 514-663-9709} ~ | ~
	\href{mailto:george.fam@famcode.net}{
	\raisebox{-0.15\height} \faEnvelope\ george.fam@famcode.net} ~ | ~
	\href{https://www.linkedin.com/in/george-fam/}{
	\raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/george-fam}
}

%---------%
% Summary %
%---------%

\tinysection{Summary}
Organized and detail-oriented Pharmacy Technician with strong experience in prescription interpretation, medication preparation, and customer service. Adept at using pharmacy management software such as RxPro, AssystRx, and Ubiq to manage prescriptions and maintain accurate records. Proven ability to work under pressure while maintaining patient safety and confidentiality. Strong communication skills, developed through extensive work in both pharmacy settings and retail settings, make me effective at collaborating with both patients and healthcare professionals. Passionate about delivering exceptional service.

%--------%
% Skills %
%--------%

\section{Skills}

\begin{multicols}{2}
	\begin{itemize}[itemsep=-2px, parsep=5pt, leftmargin=75pt]
		\item[\textbf{Pharmacy}]  RxPro, AssystRx, Ubiq, Empego, Magistral Meds, Medication Ordering, Prescription Preparation
		\item[\textbf{Soft Skills}]  Communication, Teamwork, Conflict Resolution, Active Listening, Customer Service
		\item[\textbf{Languages}]  English, French, Arabic
	\end{itemize}
\end{multicols}

%------------%
% Experience %
%------------%

\section{Experience}

\headingBf{Relief Pharmacy Technician}{Aug. 2023 -- Present}
\headingIt{BeLocum}{}
\begin{resume_list}
\item Interprets and enters prescriptions accurately using RxPro, AssystRx, and Ubiq to ensure proper medication dispensation.
\item Manages inbound inquiries, providing prompt and effective customer service to patients and healthcare professionals.
\item Accurately compounds and dispenses medications.
\item Supports pharmacies during high-volume periods, maintaining quality service and medication accuracy under pressure.
\end{resume_list}

\headingBf{Pharmacy Technician}{Sept. 2022 -- Feb. 2025}
\headingIt{Jean Coutu}{}
\begin{resume_list}
\item Processed and dispensed an average of 500 prescriptions daily using RxPro, ensuring medication accuracy and patient safety.
\item Managed medication orders and inventory, notified patients of prescription availability, and processed refills efficiently.
\end{resume_list}

\headingBf{Pharmacy Technician}{May 2021 -- Oct. 2021}
\headingIt{Uniprix}{}
\begin{resume_list}
\item Interpreted and entered prescriptions using AssystRx to ensure accurate and timely medication dispensation.
\item Assisted with medication inventory management, ensuring medications were in stock and patient orders were processed quickly.
\end{resume_list}

\headingBf{Assistant Manager}{July 2018 -- July 2020}
\headingIt{Couche-Tard}{}
\begin{resume_list}
\item Trained new team members on point-of-sale systems, customer service protocols, and inventory management.
\item Monitored daily cash intake, prepared financial reports, and made bank deposits.
\item Boosted holiday sales by 12\% through effective product promotion and sales strategies.
\end{resume_list}

%-----------%
% Education %
%-----------%

\section{Education}

\headingBf{Bachelor's Degree, Computer Science and Software Engineering}{2023 -- Ongoing}
\headingIt{UQÀM | Université de Québec à Montréal}{}
\vspace{10pt}
\headingBf{Double DEC, Science and Social Science}{2023}
\headingIt{CEGEP John Abbott}{}

\end{document}
